### 2017-09-17 ms/sum_binomials.tex
found a mistake... sigma^2 is just like in the ms

\date{\today}							% Activate to display a given date or no date

@@

\section*{Finite population model}

@@

Of the individuals with diagonally transmitted phenotypes, the number of individuals with phenotype $A$ depends only on the frequency of $A$ and random sampling, and is 
\begin{equation}
a_D \sim Bin(v, x).
\end{equation}

@@

Substituting $\frac{w_A}{\bar{w}} \to 1+\frac{s}{N}(1-x)$ (see eq.~61 in main text), we have, up to terms smaller than $1/N$,
\begin{align}
\bar{p} = 
	x(1 + \rho \frac{s}{N}(1-x))\\
\bar{p} (1-\bar{p} ) = 
	x(1-x)\Big(1 + \rho\frac{s}{N}(1-2x)\Big)\\
\frac{w_A}{\bar{w}} x - \bar{p} = 
	(1-x)\Big(1+\frac{s}{N}(1-\rho x)\Big) \\
\bar{p} - x = 
x (1-x) \rho \frac{s}{N} \\
	\Big(\frac{w_A}{\bar{w}} x - \bar{p}\Big)^2 = (1-x)^2(1 + 2\frac{s}{N}(1-\rho x)) \\
(\bar{p} - x)^2 = 0
\end{align}

So, the variance in the frequency of $A$ in the next generation $Var\Big(\frac{X_{t+1}}{N}\Big)$ given the frequency $x$ in the current generation $t$, up to terms of order smaller than $1/N$, is
\begin{equation}
\frac{1}{N^2}Var(X_{t+1}|X_t=Nx) = 
\frac{1}{N} \Big( x(1-x) - \rho (1-x)^2 \Big).
\end{equation}

Therefore, the diffusion approximation variance term $\sigma^2(x)$, is
\begin{equation}
\sigma^2(x) = x(1-x) - \rho (1-x)^2
\end{equation}
which is smaller than the value given in eq.~66 of the main text if $\rho>0$ and $0<x<1$.

>>>>

@@

\section*{Finite population model}
\textbf{\today}

@@

Of the individuals with diagonally transmitted phenotypes, the number of individuals with phenotype $A$ depends only on the frequency of $A$ and random sampling, and is 
\begin{equation}
a_D \sim Bin(N-v, x).
\end{equation}

@@

Substituting $\frac{w_A}{\bar{w}} \to 1+\frac{s}{N}(1-x)$ (see eq.~61 in main text), we have
\begin{align}
Var(X_{t+1}|X_t=Nx) = 
\frac{1}{N} x (1-x) (N^2 + N \rho s (1-2x) - \rho s^2 x (1-x)).
\end{align}

So, the variance in the frequency of $A$ in the next generation $Var\Big(\frac{X_{t+1}}{N}\Big)$ given the frequency $x$ in the current generation $t$ is
\begin{multline}
Var\Big(\frac{X_{t+1}}{N} \Big| \frac{X_{t}}{N} = x\Big) = 
\frac{1}{N^2}Var(X_{t+1}|X_t=Nx) = \\
\frac{1}{N} x (1-x) \Big(1 + \frac{1}{N} \rho s (1-2x) - \rho \frac{s^2}{N^2} x (1-x)\Big).
\end{multline}

Therefore, the diffusion approximation variance term $\sigma^2(x)$, up to terms of the order $1/N$, is
\begin{equation}
\sigma^2(x) = x(1-x),
\end{equation}
which is the same as the value given in eq.~66 of the main text if $\rho>0$ and $0<x<1$.
